---
title: "How to use the join operations from dplyr"
author: "CHEN XINRUI"
date: "October 18, 2019"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, tidy=FALSE,error=FALSE, message=FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60))
```

## Introduction
Sometimes we need to combine multiple data tables. The big direction is to merge "column" and "row". Here we mainly talk about merging "column".In this post, we will learn join function in R to combine multiple data tables.

## Prerequisites
```{r}
library(dplyr)
```


## Example
```{r, include=FALSE}
A<-read.csv("files/a.csv")
B<-read.csv("files/b.csv")
```

There are two tables.

```{r}
A
```

```{r}
B
```

Bin values of 1,2,3,4,5 are Shared by A and B; Bin with a value of 10,11,12 is unique to A; Bin with values of 6,7,8,9 is unique to B; The default is to join by common columns.

#### full_join
The number of records after using full_join equals to "the number of records in common + the number of records unique to A + the number of records unique to B". According to the join key, the number of records in common is 5, the number of records unique to A is 3, and the number of records unique to B is 4, so the sum is 12. The result can be interpreted as the union of A and B.

```{r}
full_join(A,B,by=c("chr","bin"))
```

#### inner_join

The number of records after inner_join equals to the "number of records in common", which is 5. The result can be understood as the intersection of A and B. The merge function in R language can also be implemented.

```{r}
inner_join(A,B,by=c("chr","bin"))
```

#### left_join

The number of records after left_join is equal to "the number of records of A". Of course, A needs to be put in the first parameter. 

```{r}
left_join(A,B,by=c("chr","bin"))
```


#### right_join
The number of records after right_join equals to "the number of records of B".

```{r}
right_join(A,B,by=c("chr","bin"))
```

