---
title: "How to make plots with plotly"
author: "Xinrui Chen"
date: "October 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE, tidy=FALSE,error=FALSE, message=FALSE, warning=FALSE, tidy.opts=list(width.cutoff=60))
```

## Introduction

Plotly is a technical computing company headquartered in Montreal, Quebec, that develops online data analytics and visualization tools. Plotly provides online graphing, analytics, and statistics tools for individuals and collaboration, as well as scientific graphing libraries for Python, R, MATLAB, Perl, Julia, Arduino, and REST.

In this post, we will discuss plotly for R with examples.

## Prerequisites

```{r}
library(plotly)
```

## Basic Scatter Plot

We will use iris data set to explore plotly.

```{r}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length)
p
```

## Styled Scatter Plot
```{r}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length,
        marker = list(size = 10,
                       color = 'rgba(255, 182, 193, .9)',
                       line = list(color = 'rgba(152, 0, 0, .8)',
                                   width = 2))) %>%
  layout(title = 'Styled Scatter',
         yaxis = list(zeroline = FALSE),
         xaxis = list(zeroline = FALSE))

p
```

## Plotting Markers and Lines
```{r}
trace_0 <- rnorm(100, mean = 5)
trace_1 <- rnorm(100, mean = 0)
trace_2 <- rnorm(100, mean = -5)
x <- c(1:100)

data <- data.frame(x, trace_0, trace_1, trace_2)

p <- plot_ly(data, x = ~x) %>%
  add_trace(y = ~trace_0, name = 'trace 0',mode = 'lines') %>%
  add_trace(y = ~trace_1, name = 'trace 1', mode = 'lines+markers') %>%
  add_trace(y = ~trace_2, name = 'trace 2', mode = 'markers')
p
```

## Qualitative Colorscales
```{r}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species)
p
```

## ColorBrewer Palette Names
```{r}
p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species, colors = "Set1")
p
```

## Custom Color Scales
```{r}
pal <- c("red", "blue", "green")

p <- plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species, colors = pal)
p
```

## Data Labels on Hover
```{r}
d <- diamonds[sample(nrow(diamonds), 1000), ]

p <- plot_ly(
  d, x = ~carat, y = ~price,
  # Hover text:
  text = ~paste("Price: ", price, '$<br>Cut:', cut),
  color = ~carat, size = ~carat
)
p
```





